
% Abstract
%--------------------------------------
\vspace*{45pt}
\begin{flushleft}
	{\Large \textbf{\scshape{Abstract}}}
\end{flushleft}
\vspace*{10pt}


This document aims to describe and report my experience during the curricular in-ternship completed as part of the course unit 
"Project or Internship" for the Bachelor's degree in Computer Engineering, in the Application Development track, which took place 
at The Loop Co. in the second semester of the 2023/2024 academic year.

The internship's main goal was to develop an application for the company *Zeroo Cups*. This application serves as a digital pantry, initially intended to be developed in React Native but later decided to be implemented in Ruby on Rails, with a particular focus on the mobile user experience.

The application, named Zeroo Pantry, focuses on managing the Zeroo Cups owned by the user. It allows the user to add new cups by scanning a QR code or manually entering it. From there, the user can manage the newly added cup as well as other cups they already possess. The application also offers the ability to release the cup, meaning that from the moment the cup is released, it will no longer be associated with the user, and its last event will go to the history. Additionally, there is the option to "Empty and Save," meaning that the cup will remain in the pantry but empty, and its associated event will be moved to the history. The application also includes features to consult the user's event history and the history of their cups, as well as to access information about the products associated with each cup.

The Pantry, as it is commonly called, was entirely developed in the Ruby on Rails language, using a PostgreSQL database and utilizing Hotwire, specifically the Turbo and Stimulus tools, to create a more fluid and faster user experience without the need to reload the page. Regarding the visual components of the application, ViewCompo-nents were used, which is a framework for creating reusable and modular components inspi-red by the ReactJS framework.


\vspace*{20pt}

\noindent \textbf{Keywords}:

Ruby on Rails, PostgreSQL, Hotwire, Turbo, Stimulus, ReactJS, ViewComponents.

